Waiting time analysis

### 2025-01-02 notebooks/01_results_julia.qmd
feat: add combine and remove_duplicates figure for waiting time

```{julia}
jno_df = load();
wind_df = load(; name="Wind", ts=missing);
```

@@

```{julia}
df = load_taus(; unique_f=missing)
```

```{julia}
normalize_by_max(x) = x / maximum(x)
normalize_by_max(df, x; kw...) = transform(df, x => normalize_by_max; kw...)

function plot_nrow(df, x, dx, color; xlabel=x, normalize=true, plottype=Stairs, kw...)
    y = Symbol(nrow)
    df = @chain df begin
        transform(x => ByRow(v -> round(v, dx)); renamecols=false)
        groupby([x, color]; sort=true)
        combine(nrow)
    end

    # normalize the nrows by the largest value
    if normalize
        df = normalize_by_max(groupby(df, [x]), y; renamecols=false)
        ylabel = "Relative percentage of events"
    else
        ylabel = "Number of events"
    end

    plt = data(df) * mapping(x => xlabel, y => ylabel; color) * visual(plottype)
    draw(plt; kw...)
end

plot_nrow(df, :r, 0.5, :tau; xlabel=r_lab)
easy_save("ocr/juno_tau_r")
```

>>>>

```{julia}
df = load_taus(; unique_f=missing)
jno_df = load();
wind_df = load(; name="Wind", ts=missing);
```

```{julia}
udf = Discontinuity.remove_duplicates(df)
@info nrow(udf)
@info nrow(subset(udf, :r => x -> x.>=4))
```

@@

```{julia}
normalize_by_max(x) = x / maximum(x)
normalize_by_max(df, x; kw...) = transform(df, x => normalize_by_max; kw...)
normalize_by_all(x) = x / sum(x)
normalize_by_all(df, x; kw...) = transform(df, x => normalize_by_all; kw...)

function plot_nrow(df, x, dx, color; xlabel=x, clabel=color, normalize=normalize_by_max, plottype=Stairs, kw...)
    y = Symbol(nrow)
    df = @chain df begin
        transform(x => ByRow(v -> round(v, dx)); renamecols=false)
        groupby([x, color]; sort=true)
        combine(nrow)
    end

    if normalize isa Function
        df = normalize(groupby(df, [x]), y; renamecols=false)
        ylabel = "Relative percentage of events"
    else
        ylabel = "Number of events"
    end

    plt = data(df) * mapping(x => xlabel, y => ylabel; color = color => clabel) * visual(plottype)
    draw(plt; kw...)
end

let tdf = df
    plot_nrow(tdf, :r, 0.5, :tau; xlabel=r_lab, clabel="T")
    easy_save("ocr/juno_tau_r")
end

let tdf = Discontinuity.remove_duplicates(df)
    plot_nrow(tdf, :r, 0.5, :tau; normalize = normalize_by_all, xlabel=r_lab, clabel="T")
    easy_save("ocr/juno_tau_r")
end
```

### 2025-01-02 notebooks/02_waiting_time.qmd
feat: add combine and remove_duplicates figure for waiting time

```{julia}
let step = 5
    limits = (0, 680, 5e-6, 5e-2)
    f = Figure()
    new_ax(pos; kw...) = Axis(f[pos...]; yscale=log10, xlabel="τ (minutes)", ylabel="p(τ)", limits, kw...)

    ax1 = new_ax((1, 1); xlabel="")
    plot!(WaitingTimeDist(jno_df_s1, dists, step))
    ax2 = new_ax((2, 1);)
    plot!(WaitingTimeDist(jno_df_s2, dists, step))
    axislegend(ax1, "Juno, 2011"; loc=:upperright)
    axislegend(ax2, "Juno, 2016"; loc=:upperright)
    easy_save("fig_wt_dist")
end
```

>>>>

```{julia}
function plot_fig_wt_dist(; step=5, df1=jno_df_s1, df2=jno_df_s2)
    limits = (0, 680, 5e-6, 5e-2)
    f = Figure()
    new_ax(pos; kw...) = Axis(f[pos...]; yscale=log10, xlabel="τ (minutes)", ylabel="p(τ)", limits, kw...)

    ax1 = new_ax((1, 1); xlabel="")
    plot!(WaitingTimeDist(df1, dists, step))
    ax2 = new_ax((2, 1);)
    plot!(WaitingTimeDist(df2, dists, step))
    axislegend(ax1, "Juno, 2011"; loc=:upperright)
    axislegend(ax2, "Juno, 2016"; loc=:upperright)
    return f
end

# let 
#     plot_fig_wt_dist()
#     easy_save("fig_wt_dist")
# end

let tdf = Discontinuity.remove_duplicates(df)
    df1 = subset(tdf, :time => t -> year.(t) .== 2011)
    df2 = subset(tdf, :time => t -> year.(t) .== 2016)
    plot_fig_wt_dist(; df1, df2)
    easy_save("fig_wt_dist_no_duplicates")
end
```
